Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-04-18 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
VSTTE 2020 paper update

\begin{abstract}
The use of power generation with a renewable energy source is proliferating due to industrial development. Photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation. The use of formal methods for PV systems is a new subject with significant research spanning only the last five years. Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis. We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market. Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time. We also compare our CEGIS approach with a state-of-the-art commercial tool over real PV systems to show its effectiveness.
%First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost. Second, the candidate is then verified iteratively with a lower bound cost via model checking. If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution. 
%However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. 
%\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}
\end{abstract}

>>>>

\begin{abstract}
The use of power generation with renewable energy sources is proliferating due to industrial development. Photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel energy generation. The use of formal methods for PV systems is a new subject with significant research spanning only the last five years. Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing PV systems. More specifically, we use a stand-alone configuration for this work since it is currently the most common system used for remote rural areas of developing countries or areas where the grid extension is not feasible. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach with two phases linking the technical and cost analysis. We advocate that the application of CEGIS to obtain optimal PV sizing has various advantages if compared to off-the-shelf optimization tools available in the market. Experimental results from seven case studies demonstrate that we can produce an optimal solution within an acceptable run-time. We also compare our CEGIS approach with a commercial tool specialized in PV systems optimization, with both results being simulated with an complete and accurate design software called PVsyst; furthermore, real PV systems comparison are used in order to show our approach effectiveness. 
%First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost. Second, the candidate is then verified iteratively with a lower bound cost via model checking. If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution. 
%However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. 
\keywords{Formal symthesis \and Automated verification  \and Model Checking \and Solar photovoltaic systems.}
\end{abstract}
